Continuous developmental changes in word recognition support language learning across early childhood

### 2025-09-24 paper/paper.Rmd
assorted table futzing, refs

## change to true to add optional line numbering
lineno: false
floatsintext: yes
output: papaja::apa6_pdf

@@

\begin{table*}[ht]
\centering
\begin{tabular}{rlrrrrrrrll}
  \hline
 & Dataset Name & N subjects & N Admins & Mean Age & Min Age & Max Age & Avg Trials & Avg RT Trials & CDIs & longitudinal \\ 
  \hline
1 & Yurovsky et al. (2017) & 310 & 310 & 36.82 & 12.24 & 60.00 & 6.21 & 2.87 &  &  \\ 
  2 & Yurovsky et al. (2017b) & 282 & 282 & 25.64 & 12.59 & 58.65 & 5.95 & 2.79 &  &  \\ 
  3 & Weaver \& Zettersten (2024) & 141 & 248 & 15.73 & 13.50 & 23.60 & 18.10 & 6.72 &  & x \\ 
  4 & Fernald \& Marchman (2012) & 122 & 678 & 23.92 & 17.00 & 32.00 & 16.89 & 7.21 & x & x \\ 
  5 & Sander-Montant et al. (2023) & 122 & 122 & 21.94 & 12.02 & 31.11 & 10.07 & 4.20 & x &  \\
  6 & Frank et al. (2016) & 104 & 104 & 33.89 & 12.13 & 59.84 & 5.87 & 2.74 &  &  \\ 
  7 & Baumgartner (2014) & 100 & 100 & 12.01 & 12.00 & 13.00 & 4.00 & 2.31 & x &  \\ 
  8 & Fernald et al. (2013) &  80 & 179 & 20.04 & 17.00 & 26.00 & 21.26 & 8.44 & x & x \\ 
  9 & Adams et al. (2018) &  69 & 711 & 23.58 & 13.00 & 38.00 & 18.44 & 7.92 & x & x \\ 
  10 & Potter \& Lew Williams (n.d.) &  67 &  67 & 23.76 & 21.00 & 27.00 & 10.38 & 3.80 & x &  \\ 
  11 & Fernald et al. (2006) &  63 & 229 & 19.68 & 15.00 & 25.00 & 15.25 & 6.06 & x & x \\ 
  12 & Pomper \& Saffran (n.d.) &  63 &  63 & 39.73 & 37.90 & 42.00 & 12.98 & 5.34 &  &  \\ 
  13 & Pomper \& Saffran (2016) &  60 &  60 & 44.27 & 41.00 & 47.00 & 7.55 & 3.30 &  &  \\ 
  14 & Swingley \& Aslin (2002) &  50 &  50 & 15.09 & 14.13 & 16.00 & 11.74 & 3.79 & x &  \\ 
  15 & Pomper \& Saffran (2019) &  44 &  44 & 40.11 & 38.00 & 43.00 & 5.30 & 2.34 &  &  \\ 
  16 & Perry \& Saffan (2017) &  42 &  42 & 20.45 & 19.00 & 22.00 & 14.88 & 5.43 & x &  \\ 
  17 & Ronfard, Wei, \& Rowe (2022) &  40 &  40 & 19.95 & 18.00 & 24.00 & 18.54 & 7.62 & x &  \\ 
  18 & Bacon \& Saffran (2022) &  38 &  38 & 22.87 & 22.00 & 24.00 & 18.16 & 8.00 & x &  \\ 
  19 & Garrison \& Bergelson (2020) &  35 &  35 & 14.46 & 12.00 & 18.00 & 27.47 & 9.41 & x &  \\ 
  20 & Pomper \& Saffran (n.d.) &  32 &  32 & 26.38 & 25.00 & 28.00 & 7.62 & 2.31 &  &  \\ 
  21 & Mahr et al. (2015) & 29 &  29 & 20.83 & 18.10 & 23.80 & 24.38 & 8.86 & x &  \\ 
  22 & Ferguson, Graf, \& Waxman (2014) & 28 &  28 & 19.71 & 18.02 & 21.86 & 5.54 & 2.33 & x &  \\ 
  23 & Potter et al. (2019) &  23 &  44 & 22.59 & 18.00 & 29.00 & 6.07 & 2.58 & x & x \\ 
  24 & Newman \& Morini (2017)  &  19 &  19 & 30.12 & 29.23 & 30.84 & 13.11 & 4.94 &  &  \\ 
  \hline
    & Total & 1963 & 3554 & 24.73 & 12.00 & 60.00 & 12.74 & 5.05 & 15 & 6 \\ 
   \hline
\end{tabular}
\caption{Characteristics of included datasets from Peekbank. "Admins" denotes separate experimental sessions. "CDIs" refers to whether the dataset contains parent report vocabulary data from the MacArthur-Bates Communicative Development Inventory. \label{tab:datasets}} 
\end{table*}

@@

We investigate two specific hypotheses here. First, one influential theory posits that language learning is a process of skill learning, in which the child is learning the skill of fluent conversation with other language users [@christiansen2016;@chater2018]. In this theory, the major information processing challenge of language learning is that incoming language is ephemeral and must be processed quickly before it is lost (the "now-or-never bottleneck"). On this kind of account, we should expect to see the signatures of expertise and skill learning in word recognition, which is one of the primary skills involved in processing incoming language in real time. Accuracy should change linearly with the logarithm of age, reflecting gradual asymptotic convergence to mature levels of accuracy. In addition, we might observe what is known as the "power law of practice," the regularity found in many cases of skill learning that the logarithm of reaction time decreases with the logarithm of experience across participants [@snoddy1926;@kail1991;@anderson1982; cf. @heathcote2000; @heathcote2018]. Indeed, this pattern is predicted by an influential associative process model of early word learning [@mcmurray2012].  In our case, we expect that chronological age is a proxy for experience and so the logarithm of reaction time should decrease linearly with the logarithm of age. Finally, trial-to-trial variability in both speed and accuracy should decrease with increasing expertise, as is found in studies of motor expertise [@todorov2002optimal].

@@

```{r loading, echo=FALSE, message=FALSE, warning=FALSE}
suppressPackageStartupMessages(library(here))
suppressPackageStartupMessages(library(psych))
suppressPackageStartupMessages(library(lmerTest))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tidySEM))
suppressPackageStartupMessages(library(xtable))
suppressPackageStartupMessages(library(papaja))
suppressPackageStartupMessages(library(viridis))
suppressPackageStartupMessages(library(nlme))
suppressPackageStartupMessages(library(cowplot))

@@

```{r devchange, fig.cap="Participant-level target looking and reaction time (log), plotted by age (log). Longitudinal datapoints are connected by lines. The solid blue line shows a linear fit and associated confidence interval. Thin colored lines show linear fits for those datasets spanning six or more months of age. The dashed line for accuracy shows chance-level looking (.5)", fig.env="figure*", fig.height = 2.5}

@@

```{r variance, fig.cap="Participant-level variability in target looking and reaction time (log RT), plotted by age (log). Plotting conventions are as in Figure 1.", fig.env="figure*", fig.height = 2.5}
  mycolors = c("#1B9E77", "#D95F02", "#E7298A", "#66A61E", "#1B9E77", "#D95F02", "#E7298A", "#66A61E", "#1B9E77", "#D95F02", "#E7298A", "#66A61E","#1B9E77", "#D95F02")

@@

```{r age-regression, fig.env="figure*", fig.cap="Structural equation model showing the three-factor factor analysis with a regression of each latent variable on the logarithm of age. Observed variables are notated as squares and latent variables are notated as circles Factor loadings and regression coefficients are shown with straight, solid lines; covariances are shown with dashed lines; residual variances are shown as solid circular connections. Stars show conventional levels of statistical significance, e.g. * indicates p < .05, ** indicates p < .01, and *** indicates p < .001. Covariances reflect age-residualized correlations between variables.", fig.height = 3}

@@

```{r growth, fig.cap="Growth curves from a logistic growth model showing predicted vocabulary growth for the 25th (red) and 75th (blue) percentile on initial reaction times. Individual longitudinal trajectories are shown in light gray. Solid lines show global model estimates and dashed lines show estimates for individual datasets with sufficient age variation as above.", fig.env="figure", fig.height = 2.5, fig.width=4, out.width=".5\\textwidth", include=TRUE}

d_sub_prod <- filter(d_sub, !is.na(prod)) |>
  group_by(subject_id) |>
  mutate(log_rt_0 = log_rt[1],
         acc_0 = long_window_accuracy[1]) |> 
  filter(!is.na(log_rt_0))

mod_nlme <- nlme(model = prod ~ SSlogis(age, Asym = 1, xmid, scale),
             data = d_sub_prod,
             fixed = xmid + scale ~ log_rt_0,
             random = xmid + scale ~ 1 | subject_id,
             groups = ~ dataset_name,
             start = c(xmid = 20, scale = 3, `xmid:log_rt_0` = 1, `scale:log_rt_0` = 3),
             na.action = na.exclude, 
             control = list(maxIter = 1000, tolerance = 10))

# fixed effects (no CIs)
global_preds <- expand_grid(age = seq(min(d_sub_prod$age), 
                                      max(d_sub_prod$age), .1), 
                            log_rt_0 = c(quantile(d_sub_prod$log_rt, 
                                                  c(.25,.75), 
                                                  na.rm=TRUE)))
global_preds$pred <- predict(mod_nlme, newdata = global_preds, level = 0)

#random effects
dataset_preds <- d_sub |>
  filter(!is.na(prod)) |> # filter on predictor
  group_by(dataset_name) |>
  summarise(min_age = min(age),
            max_age = max(age)) |>
  group_by(dataset_name) |>
  mutate(df = map2(min_age, max_age, ~expand_grid(age = seq(.x, .y, .1), log_rt_0 = c(quantile(d_sub_prod$log_rt_0, 
                                                  c(.25,.75), 
                                                  na.rm=TRUE))))) |>
  select(-min_age, -max_age) |>
  unnest(col = "df") |>
  ungroup()

dataset_preds$pred <- predict(mod_nlme,
                              newdata = dataset_preds,
                              level = c(0,1))$predict.dataset_name

ggplot(d_sub_prod, aes(x = age, y = prod, col = as.factor(log_rt_0))) + 
  geom_point(alpha = .03, pch = ".", col = "black") + 
  geom_line(aes(group = subject_id), alpha = .02, col = "black") + 
  geom_line(data = dataset_preds |>   
              filter(dataset_name %in% datasets_with_age_variation$dataset_name), 
            aes(y = pred, group = interaction(log_rt_0, dataset_name)), lty="dashed", alpha=.5)+
  geom_line(data = global_preds, aes(y = pred, group = log_rt_0, col = as.factor(log_rt_0)), size=1)+
  scale_color_viridis(discrete=T, option = "H")+
  theme(legend.position = "none")+
  labs(y="Production", x="Age in months")
# +
#   geom_line(data = dataset_preds, aes(y = pred))
```

@@

```{r longitudinal, fig.env="figure*", height = 3.5, fig.cap = "Structural equation model showing longitudinal couplings between growth parameters. "}
layout <- read.csv(here("misc/layout_slopes_observed_growth.csv"), header = FALSE)

@@

Reaction times

@@

We used `lme4` to fit linear mixed effects models, `nlme` to fit non-linear models, and `lavaan` to fit structural equation models. Random effects structures for each model are given in text; full model specifications are available in the Supplemental Information and in the reproducible code for this paper, available in the linked repository. To aid interpretability, all variables were standardized (z-scored) prior to inclusion in structural equation models.

>>>>

## change to true to add optional line numbering
lineno: false
floatsintext: yes
output: papaja::apa6_pdf
header-includes:
  - \usepackage{threeparttablex}
  - \usepackage{booktabs}
  - \usepackage{placeins}
  - \usepackage{float}
  - \renewcommand{\textfraction}{0.00}
  - \renewcommand{\topfraction}{1}
  - \renewcommand{\bottomfraction}{1}
  - \renewcommand{\floatpagefraction}{1}
  - \setcounter{topnumber}{5}
  - \setcounter{bottomnumber}{5}
  - \setcounter{totalnumber}{6}

@@

\begin{table}[ht]
\centering
\setlength\tabcolsep{2pt}
\begin{scriptsize}
\begin{tabular}{rlrrrrrrrll}
  \hline
 & Dataset Name & N subjects & N Admins & Mean Age & Min Age & Max Age & Avg Trials & Avg RT Trials & CDIs & longitudinal \\ 
  \hline
1 & Yurovsky et al. (2017) & 310 & 310 & 36.82 & 12.24 & 60.00 & 6.21 & 2.87 &  &  \\ 
  2 & Yurovsky et al. (2017b) & 282 & 282 & 25.64 & 12.59 & 58.65 & 5.95 & 2.79 &  &  \\ 
  3 & Weaver \& Zettersten (2024) & 141 & 248 & 15.73 & 13.50 & 23.60 & 18.10 & 6.72 &  & x \\ 
  4 & Fernald \& Marchman (2012) & 122 & 678 & 23.92 & 17.00 & 32.00 & 16.89 & 7.21 & x & x \\ 
  5 & Sander-Montant et al. (2023) & 122 & 122 & 21.94 & 12.02 & 31.11 & 10.07 & 4.20 & x &  \\
  6 & Frank et al. (2016) & 104 & 104 & 33.89 & 12.13 & 59.84 & 5.87 & 2.74 &  &  \\ 
  7 & Baumgartner (2014) & 100 & 100 & 12.01 & 12.00 & 13.00 & 4.00 & 2.31 & x &  \\ 
  8 & Fernald et al. (2013) &  80 & 179 & 20.04 & 17.00 & 26.00 & 21.26 & 8.44 & x & x \\ 
  9 & Adams et al. (2018) &  69 & 711 & 23.58 & 13.00 & 38.00 & 18.44 & 7.92 & x & x \\ 
  10 & Potter \& Lew Williams (n.d.) &  67 &  67 & 23.76 & 21.00 & 27.00 & 10.38 & 3.80 & x &  \\ 
  11 & Fernald et al. (2006) &  63 & 229 & 19.68 & 15.00 & 25.00 & 15.25 & 6.06 & x & x \\ 
  12 & Pomper \& Saffran (n.d.) &  63 &  63 & 39.73 & 37.90 & 42.00 & 12.98 & 5.34 &  &  \\ 
  13 & Pomper \& Saffran (2016) &  60 &  60 & 44.27 & 41.00 & 47.00 & 7.55 & 3.30 &  &  \\ 
  14 & Swingley \& Aslin (2002) &  50 &  50 & 15.09 & 14.13 & 16.00 & 11.74 & 3.79 & x &  \\ 
  15 & Pomper \& Saffran (2019) &  44 &  44 & 40.11 & 38.00 & 43.00 & 5.30 & 2.34 &  &  \\ 
  16 & Perry \& Saffan (2017) &  42 &  42 & 20.45 & 19.00 & 22.00 & 14.88 & 5.43 & x &  \\ 
  17 & Ronfard, Wei, \& Rowe (2022) &  40 &  40 & 19.95 & 18.00 & 24.00 & 18.54 & 7.62 & x &  \\ 
  18 & Bacon \& Saffran (2022) &  38 &  38 & 22.87 & 22.00 & 24.00 & 18.16 & 8.00 & x &  \\ 
  19 & Garrison \& Bergelson (2020) &  35 &  35 & 14.46 & 12.00 & 18.00 & 27.47 & 9.41 & x &  \\ 
  20 & Pomper \& Saffran (n.d.) &  32 &  32 & 26.38 & 25.00 & 28.00 & 7.62 & 2.31 &  &  \\ 
  21 & Mahr et al. (2015) & 29 &  29 & 20.83 & 18.10 & 23.80 & 24.38 & 8.86 & x &  \\ 
  22 & Ferguson, Graf, \& Waxman (2014) & 28 &  28 & 19.71 & 18.02 & 21.86 & 5.54 & 2.33 & x &  \\ 
  23 & Potter et al. (2019) &  23 &  44 & 22.59 & 18.00 & 29.00 & 6.07 & 2.58 & x & x \\ 
  24 & Newman \& Morini (2017)  &  19 &  19 & 30.12 & 29.23 & 30.84 & 13.11 & 4.94 &  &  \\ 
  \hline
    & Total & 1963 & 3554 & 24.73 & 12.00 & 60.00 & 12.74 & 5.05 & 15 & 6 \\ 
   \hline
\end{tabular}
\end{scriptsize}
\caption{Characteristics of included datasets from Peekbank. "Admins" denotes separate experimental sessions. "CDIs" refers to whether the dataset contains parent report vocabulary data from the MacArthur-Bates Communicative Development Inventory. \label{tab:datasets}} 
\end{table}

@@

We investigate two specific hypotheses here. First, one influential theory posits that language learning is a process of skill learning, in which the child is learning the skill of fluent conversation with other language users [@christiansen2016;@chater2018]. In this theory, the major information processing challenge of language learning is that incoming language is ephemeral and must be processed quickly before it is lost (the "now-or-never bottleneck"). On this kind of account, we should expect to see the signatures of expertise and skill learning in word recognition, which is one of the primary skills involved in processing incoming language in real time. Accuracy should change linearly with the logarithm of age, reflecting gradual asymptotic convergence to mature levels of accuracy. In addition, we might observe what is known as the "power law of practice," the regularity found in many cases of skill learning that the logarithm of reaction time decreases with the logarithm of experience across participants [@snoddy1926;@kail1991;@anderson1982; cf. @heathcote2000; @heathcote2018, @evans2018]. Indeed, this pattern is predicted by an influential associative process model of early word learning [@mcmurray2012].  In our case, we expect that chronological age is a proxy for experience and so the logarithm of reaction time should decrease linearly with the logarithm of age. Finally, trial-to-trial variability in both speed and accuracy should decrease with increasing expertise, as is found in studies of motor expertise [@todorov2002optimal].

@@

```{r loading, echo=FALSE, message=FALSE, warning=FALSE}
suppressPackageStartupMessages(library(here))
suppressPackageStartupMessages(library(psych))
suppressPackageStartupMessages(library(lmerTest))
suppressPackageStartupMessages(library(lavaan))
suppressPackageStartupMessages(library(tidySEM))
suppressPackageStartupMessages(library(xtable))
suppressPackageStartupMessages(library(papaja))
suppressPackageStartupMessages(library(viridis))
#suppressPackageStartupMessages(library(nlme))
suppressPackageStartupMessages(library(cowplot))

@@

```{r devchange, fig.cap="Participant-level target looking and reaction time (log), plotted by age (log). Longitudinal datapoints are connected by lines. The solid blue line shows a linear fit and associated confidence interval. Thin colored lines show linear fits for those datasets spanning six or more months of age. The dashed line for accuracy shows chance-level looking (.5)", fig.env="figure", fig.height = 2.5}

@@

```{r variance, fig.cap="Participant-level variability in target looking and reaction time (log RT), plotted by age (log). Plotting conventions are as in Figure 1.", fig.env="figure", fig.height = 2.5}
  mycolors = c("#1B9E77", "#D95F02", "#E7298A", "#66A61E", "#1B9E77", "#D95F02", "#E7298A", "#66A61E", "#1B9E77", "#D95F02", "#E7298A", "#66A61E","#1B9E77", "#D95F02")

@@

```{r age-regression, fig.env="figure", fig.cap="Structural equation model showing the three-factor factor analysis with a regression of each latent variable on the logarithm of age. Observed variables are notated as squares and latent variables are notated as circles Factor loadings and regression coefficients are shown with straight, solid lines; covariances are shown with dashed lines; residual variances are shown as solid circular connections. Stars show conventional levels of statistical significance, e.g. * indicates p < .05, ** indicates p < .01, and *** indicates p < .001. Covariances reflect age-residualized correlations between variables.", fig.height = 3}

@@

```{r}
d_sub_prod <- filter(d_sub, !is.na(prod), !is.na(log_rt)) |>
  ungroup() |>
  mutate(log_rt_resid = resid(lm(log_rt ~ log_age))) |>
  group_by(subject_id) |>
  mutate(log_rt_0 = log_rt[1],
         log_rt_0_resid = log_rt_resid[1],
         acc_0 = long_window_accuracy[1]) |> 
  filter(!is.na(log_rt_0))

d_sub_prod$age_c <- d_sub_prod$age - mean(d_sub_prod$age, na.rm = TRUE)
d_sub_prod$log_rt_0_c <- d_sub_prod$log_rt_0 - mean(d_sub_prod$log_rt_0, na.rm = TRUE)
```

```{r, eval=F}
library(brms)

# Define the nonlinear formula
nlform <- brms::bf(
  prod ~ 1 / (1 + exp((xmid - age_c) / exp(logscale))),
  xmid ~ 1 + log_rt_0_c  + (1 | dataset_name/subject_id),
  logscale ~ 1 + log_rt_0_c  + (1 | dataset_name/subject_id),
  # scale ~ 1 + log_rt_0_c,
  nl = TRUE
)

# xmid ~ 1 + log_rt_0_c + (1 | dataset_name/subject_id),
# scale ~ 1 + log_rt_0_c + (1 | dataset_name/subject_id),

priors <- c(
  prior(normal(0, 5), nlpar = "xmid", coef = "Intercept"),  # xmid near center of age_c
  prior(normal(1, 1), nlpar = "logscale", coef = "Intercept"), # scale > 0, mildly steep curve
  prior(normal(0, 1), nlpar = "logscale", coef = "log_rt_0_c"),
  prior(exponential(1), class = "sigma"),                # residual error
  prior(normal(0, 2), nlpar = "xmid", coef = "log_rt_0_c"),
  # prior(normal(0, 1), nlpar = "scale", lb = 0)

  # Random effects for xmid
  prior(exponential(1), class = "sd", nlpar = "xmid", group = "dataset_name"),
  prior(exponential(1), class = "sd", nlpar = "xmid", group = "dataset_name:subject_id"),

  # Random effects for scale
  prior(exponential(1), class = "sd", nlpar = "logscale", group = "dataset_name"),
  prior(exponential(1), class = "sd", nlpar = "logscale", group = "dataset_name:subject_id")
)
#

# Fit the model
mod_brms <- brm(
  formula = nlform,
  data = d_sub_prod,
  prior = priors,
  family = gaussian(),
  # init = 0,  # initialize all parameters to 0 on unconstrained scale (safe for centered priors)
  chains = 4, cores = 4,
  control = list(adapt_delta = 0.95),
  # backend = "cmdstanr",  # optional but faster
  save_pars = save_pars(all = TRUE),
  sample_prior = "yes",
  file="brms1.rds"
)

summary(mod_brms)$fixed |> saveRDS("brms1_coef.rds")

new_data <- expand.grid(
  age_c = seq(min(d_sub_prod$age_c), max(d_sub_prod$age_c), length.out = 100),
  log_rt_0_c = c(-1, 0, 1)  # e.g., low, mean, high values
)

fitted_vals <- fitted(mod_brms, newdata = new_data, re_formula = NA, summary = TRUE)

saveRDS(fitted_vals, "brms1_fitted.rds")

```

```{r growth, fig.cap="Growth curves from a logistic growth model showing predicted vocabulary growth for children with initial reaction times one SD faster than the mean (blue), at the mean (red), and one SD slower than the mean (green). Individual longitudinal trajectories are shown in light gray. Solid lines show global model estimates and colored regions indicate 95% credible intervals.", fig.env="figure", fig.height = 4, fig.width=6, out.width=".6\\textwidth", include=TRUE}

fitted_vals <- readRDS("brms1_fitted.rds")

new_data <- expand.grid(
  age_c = seq(min(d_sub_prod$age_c), max(d_sub_prod$age_c), length.out = 100),
  log_rt_0_c = c(-1, 0, 1)  # e.g., low, mean, high values
)

new_data$fit <- fitted_vals[, "Estimate"]
new_data$lower <- fitted_vals[, "Q2.5"]
new_data$upper <- fitted_vals[, "Q97.5"]

ggplot(new_data, aes(x = age_c, y = fit, col = as.factor(log_rt_0_c))) +
    geom_line(data = d_sub_prod, aes(x = age_c, y = prod, group=subject_id), col = "black", alpha=.1) + 
  geom_line(linewidth = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = as.factor(log_rt_0_c), group = as.factor(log_rt_0_c)), 
              alpha = 0.3) +
  labs(x = "Centered Age", y = "Predicted prod (fixed effects only)") +
  theme_minimal() + 
  scale_color_solarized(name = "log RT at t0 (SD)") + 
  scale_fill_solarized(guide = FALSE)

```

@@

```{r longitudinal, fig.env="figure", height = 3.5, fig.cap = "Structural equation model showing longitudinal couplings between growth parameters. "}
layout <- read.csv(here("misc/layout_slopes_observed_growth.csv"), header = FALSE)

@@

@@

We used `lme4` to fit linear mixed effects models, `brms` to fit non-linear growth models, and `lavaan` to fit structural equation models. Random effects structures for each model are given in text; full model specifications are available in the Supplemental Information and in the reproducible code for this paper, available in the linked repository. To aid interpretability, all variables were standardized (z-scored) prior to inclusion in structural equation models.
